### 2019-09-20 journal/ms.tex
revisions

What factors shape vocabulary learning over the course of early
childhood? To investigate this question, scientists have adopted
multiple research strategies, from conducting controlled laboratory
experiments (e.g. Markman, 1990) to analyzing dense corpora capturing
language learning in context (e.g., B. C. Roy, Frank, DeCamp, Miller, \&
Roy, 2015). One prominent strategy consists in documenting the timeline
of words' acquisition, and studying the properties that make words easy
or hard to learn (e.g., J. C. Goodman, Dale, \& Li, 2008; Huttenlocher,
Haight, Bryk, Seltzer, \& Lyons, 1991). For example, J. C. Goodman et
al. (2008) found that, within a lexical category (e.g., nouns), higher
parental frequency is associated with earlier learning. Researchers have
studied the role of several other factors such as word length and the
mean length of utterances in which the word occurs (e.g., Braginsky,
Yurovsky, Marchman, \& Frank, in revision; Swingley \& Humphrey, 2018).

@@

\caption{Illustration of the two growth scenarios. Filled grey circles represent known words (Internal) at a certain point in time. The empty, numbered circles represent words that have not yet been learned (External) and which are candidates to enter the lexicon next. The identity of the word that is going to be learned depends on the growth scenario.  Here the squares indicate the node that drives growth in each scenario and the hand pointer indicates which word is likely to be learned. For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to INT, node 1 is more likely to enter the lexicon. For EXT, the utility of a candidate node is its degree in the entire network. According to EXT, node 2 is more likely to enter the lexicon next. This figure is based on an example from Hills et al (2009).}\label{fig:growth}
\end{figure}

@@

Second, we study vocabularies measured using both comprehension and
production. Previous studies have found differences between these
vocabularies in terms of their content and rate of acquisition (Bates,
Dale, \& Thal, 1995; Benedict, 1979; Fenson et al., 1994). These
differences may reflect the fact that comprehension and production do
not share the same constraints. For instance, whereas comprehension
depends on the ease with which words are stored and accessed, production
depends, additionally, on the ease with which words are articulated,
e.g., shorter words are produced earlier (Braginsky et al., in
revision). By investigating comprehension-based vocabularies, we assess
the extent to which the network growth mechanism captures general
learning patterns beyond the specific constraints of production.

@@

For each word in the CDI data, we compute the proportion of children who
understand or produce the word at each month. Then we fit a logistic
curve to these proportions and determined when the curve crosses 0.5,
i.e., the age at which at least 50\% of children know the word. We take
this point in time to be each word's age of acquisition (Braginsky et
al., in revision; J. C. Goodman et al., 2008).

@@

\caption{\label{tab:stats}Statistics for the dataset we used.}
\centering
\begin{tabular}[t]{>{\bfseries}lrlrrlr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{3}{c}{Comprehension} & \multicolumn{3}{c}{Production} \\
\cmidrule(l{2pt}r{2pt}){2-4} \cmidrule(l{2pt}r{2pt}){5-7}
Language & Nouns & Ages & N & Nouns & Ages & N\\
\midrule
Croatian & 209 & 8-16 & 250 & 312 & 16-30 & 377\\
Danish & 200 & 8-20 & 2,398 & 316 & 16-36 & 3,714\\
English & 209 & 8-18 & 2,435 & 312 & 16-30 & 5,520\\
French & 197 & 8-16 & 537 & 307 & 16-30 & 827\\
Italian & 209 & 7-24 & 648 & 312 & 18-36 & 752\\
Norwegian & 193 & 8-20 & 2,922 & 316 & 16-36 & 9,303\\
Russian & 207 & 8-18 & 768 & 314 & 18-36 & 1,037\\
Spanish & 208 & 8-18 & 788 & 312 & 16-30 & 1,146\\
Swedish & 205 & 8-16 & 467 & 339 & 16-28 & 900\\
Turkish & 180 & 8-16 & 1,115 & 297 & 16-36 & 2,422\\
\bottomrule
\end{tabular}
\end{table}

@@

Above we showed that the way semantic and phonological information is
structured in the learning environment contributes to noun learning (via
EXT) across languages. However, we know that other factors influence
learning as well (e.g., Braginsky et al., in revision). Next we
investigated how semantic and phonological connectivity interact with
two other factors. The first one is word frequency, a well studied
factor shown to predict the age of acquisition in a reliable fashion
(e.g. J. C. Goodman et al., 2008). The second factor is word length,
which was shown to correlate with phonological connectivity: Shorter
words are more likely to have higher connectivity (Pisoni, Nusbaum,
Luce, \& Slowiaczek, 1985; Vitevitch \& Rodríguez, 2005).

@@

For word length, we counted the number of phonemes in our generated IPA
transcription. For word frequency, we used the frequency estimates from
Braginsky et al. (in revision) where unigram counts were derived based
on CHILDES corpora in each language (MacWhinney, 2014). Although these
frequency counts use transcripts from independent sets of children, they
are based on large samples, and this allows us to average out possible
differences between children and the specificities of their input (see
J. C. Goodman et al., 2008 for a similar research strategy).

@@

The findings for the new predictors were as follows. Overall, frequency
is the largest and most consistent predictor of age of acquisition in
both comprehension and production data and across languages, endorsing
results for nouns across a variety of analyses (Braginsky et al., in
revision; J. C. Goodman et al., 2008; B. C. Roy et al., 2015). Word
length is more predictive for production than comprehension (and this
difference is very clear in the global model), replicating previous work
(Braginsky et al., in revision). Thus, word length seems to reflect the
effects of production's constraints rather than comprehension's
constraints, i.e., longer words are harder to articulate but they may
not be significantly more difficult to store and access.

@@

In the phonological case, network growth according to EXT is also
compatible with a scenario whereby children are tracking low level
statistical patterns, e.g., high probability sound sequences. Indeed,
connectivity in the phonological network is inherently correlated with
phonotactic probability (Vitevitch, Luce, Pisoni, \& Auer, 1999). That
is, highly connected words tend to be made of frequent sound sequences.
Children are sensitive to local phonotactic regularities (Jusczyk, Luce,
\& Charles-Luce, 1994) and this sensitivity might lead them to learn
higher-probability words more easily (Storkel, 2001). This explanation
is supported by computational simulations that show how learning general
phonotactics patterns create \enquote{well-worn paths} which allow the
models to represent several distinct but phonologically neighboring
words (Dell, Juliano, \& Govindjee, 1993; Takac, Knott, \& Stokes,
2017).

@@

This work shares a number of limitations with previous studies using
similar research strategy and datasets. Chief among these limitations is
the fact that the age of word acquisition is computed using different
children at different ages (due to the fact that available CDI data is
mainly cross-sectional). Such a measure has been shown to be valid and
reliable (Fenson et al., 1994), and has allowed researchers to study
important aspects of word learning (Braginsky et al., in revision; J. C.
Goodman et al., 2008; Hills et al., 2009; Stella et al., 2017; Storkel,
2009). In our case, the use of cost-effective cross-sectional data has
allowed us to leverage large-scale studies across several languages.
That said, it is important to remember that this type of data can only
inform us about the learning trajectory of the \enquote{average} child.
Although our study endorses, overall, the externally-driven account of
network growth, this does not mean individual children never use some
variant of INT or some combination of both INT and EXT (Beckage \&
Colunga, under review). To illustrate, some children develop
\enquote{islands of expertise}, that is, well organized knowledge about
a certain topic (e.g., birds or dinosaurs). This prior knowledge enables
these children to learn new related words more easily (e.g., Chi \&
Koeske, 1983).

@@

\section{Appendix}\label{appendix}

\subsection{Edit 1}\label{edit-1}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlot-1} \caption{Production data (Age of acquisition) as predicted by the degree (i.e., connectivity) in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrPlot}
\end{figure}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllEdit-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect. Results are shown for both production and comprehension data. Ranges indicate 95\% confidence intervals. Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.}\label{fig:staticAllEdit}
\end{figure}

\subsection{Continuous edit distance}\label{continuous-edit-distance}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllnt-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined mixed-effects model with language as a random effect. Results are shown for both production and comprehension data. Ranges indicate 95\% confidence intervals. Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.}\label{fig:staticAllnt}
\end{figure}

@@

@@

@@

\hypertarget{ref-braginsky}{}
Braginsky, M., Yurovsky, D., Marchman, V. A., \& Frank, M. C. (in
revision). Consistency and variability in word learning across
languages.

@@

@@

@@

@@

>>>>

What factors shape vocabulary learning over the course of early
childhood? To investigate this question, scientists have adopted
multiple research strategies, from conducting controlled laboratory
experiments (e.g. Markman, 1990) to analyzing dense corpora capturing
language learning in context (e.g., B. C. Roy, Frank, DeCamp, Miller, \&
Roy, 2015). One prominent strategy consists in documenting the timeline
of words' acquisition, and studying the properties that make words easy
or hard to learn (e.g., J. C. Goodman, Dale, \& Li, 2008; Huttenlocher,
Haight, Bryk, Seltzer, \& Lyons, 1991). For example, J. C. Goodman et
al. (2008) found that, within a lexical category (e.g., nouns), higher
parental frequency is associated with earlier learning. Researchers have
studied the role of several other factors such as word length and the
mean length of utterances in which the word occurs (e.g., Braginsky,
Yurovsky, Marchman, \& Frank, 2019; D. Swingley \& Humphrey, 2018).

@@

\caption{Illustration of the two growth scenarios. Filled grey circles represent known words (Internal) at a certain point in time. The empty, numbered circles represent words that have not yet been learned (External) and which are candidates to enter the lexicon next. The identity of the word that is going to be learned depends on the growth scenario.  Here the squares indicate the node that drives growth in each scenario and the hand pointer indicates which word is likely to be learned. For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. In this simplified example, candidate node 1 would connect to an internal node with 3 connections, thus we have $u_{INT}(node_1)= 3$. As for candidate node 2, it would connect to internal nodes that have only one connection each, making an average of 1, i.e., $u_{INT}(node_2)= 1$. According to INT, node 1 is more likely to enter the lexicon. For EXT, the utility of a candidate node is its degree in the entire network. In our example, candidate node 1 has 2 connections in total whereas candidate node 2 has 5 connections. So we have $u_{EXT}(node_1)= 2$ and $u_{EXT}(node_2)= 5$. Thus, according to EXT, node 2 is more likely to enter the lexicon next. This figure is based on an example from Hills et al. (2009).}\label{fig:growth}
\end{figure}

@@

Second, we study vocabularies measured using both comprehension and
production. Previous studies have found differences between these
vocabularies in terms of their content and rate of acquisition (Bates,
Dale, \& Thal, 1995; Benedict, 1979; Fenson et al., 1994). These
differences may reflect the fact that comprehension and production do
not share the same constraints. For instance, whereas comprehension
depends on the ease with which words are stored and accessed, production
depends, additionally, on the ease with which words are articulated,
e.g., shorter words are produced earlier (Braginsky et al., 2019). By
investigating comprehension-based vocabularies, we assess the extent to
which the network growth mechanism captures general learning patterns
beyond the specific constraints of production.

@@

For each word in the CDI data, we compute the proportion of children who
understand or produce the word at each month. Then we fit a logistic
curve to these proportions and determined when the curve crosses 0.5,
i.e., the age at which at least 50\% of children know the word. We take
this point in time to be each word's age of acquisition (Braginsky et
al., 2019; J. C. Goodman et al., 2008).

@@

\caption{\label{tab:stats}Statistics for the dataset we used. The ages are in months.}
\centering
\begin{tabular}[t]{>{\bfseries}lrlrrlr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{3}{c}{Comprehension} & \multicolumn{3}{c}{Production} \\
\cmidrule(l{2pt}r{2pt}){2-4} \cmidrule(l{2pt}r{2pt}){5-7}
Language & Nouns & Ages & N & Nouns & Ages & N\\
\midrule
Croatian & 209 & 8-16 & 250 & 312 & 16-30 & 377\\
Danish & 200 & 8-20 & 2,398 & 316 & 16-36 & 3,714\\
English & 209 & 8-18 & 2,435 & 312 & 16-30 & 5,520\\
French & 197 & 8-16 & 537 & 307 & 16-30 & 827\\
Italian & 209 & 7-24 & 648 & 312 & 18-36 & 752\\
Norwegian & 193 & 8-20 & 2,922 & 316 & 16-36 & 9,303\\
Russian & 207 & 8-18 & 768 & 314 & 18-36 & 1,037\\
Spanish & 208 & 8-18 & 788 & 312 & 16-30 & 1,146\\
Swedish & 205 & 8-16 & 467 & 339 & 16-28 & 900\\
Turkish & 180 & 8-16 & 1,115 & 297 & 16-36 & 2,422\\
\bottomrule
\end{tabular}
\end{table}

@@

Above we showed that the way semantic and phonological information is
structured in the learning environment contributes to noun learning (via
EXT) across languages. However, we know that other factors influence
learning as well (e.g., Braginsky et al., 2019). Next we investigated
how semantic and phonological connectivity interact with two other
factors. The first one is word frequency, a well studied factor shown to
predict the age of acquisition in a reliable fashion (e.g. J. C. Goodman
et al., 2008). The second factor is word length, which was shown to
correlate with phonological connectivity: Shorter words are more likely
to have higher connectivity (Pisoni, Nusbaum, Luce, \& Slowiaczek, 1985;
Vitevitch \& Rodríguez, 2005).

@@

For word length, we counted the number of phonemes in our generated IPA
transcription. For word frequency, we used the frequency estimates from
Braginsky et al. (2019) where unigram counts were derived based on
CHILDES corpora in each language (MacWhinney, 2014). Although these
frequency counts use transcripts from independent sets of children, they
are based on large samples, and this allows us to average out possible
differences between children and the specificities of their input (see
J. C. Goodman et al., 2008 for a similar research strategy).

@@

The findings for the new predictors were as follows. Overall, frequency
is the largest and most consistent predictor of age of acquisition in
both comprehension and production data and across languages, endorsing
results for nouns across a variety of analyses (Braginsky et al., 2019;
J. C. Goodman et al., 2008; B. C. Roy et al., 2015). Word length is more
predictive for production than comprehension (and this difference is
very clear in the global model), replicating previous work (Braginsky et
al., 2019). Thus, word length seems to reflect the effects of
production's constraints rather than comprehension's constraints, i.e.,
longer words are harder to articulate but they may not be significantly
more difficult to store and access.

@@

In the phonological case, network growth according to EXT is also
compatible with a scenario whereby children are tracking low level
statistical patterns, e.g., high probability sound sequences. Indeed,
connectivity in the phonological network is inherently correlated with
phonotactic probability (Vitevitch, Luce, Pisoni, \& Auer, 1999). That
is, highly connected words tend to be made of frequent sound sequences.
Children are sensitive to local phonotactic regularities (Jusczyk, Luce,
\& Charles-Luce, 1994) and this sensitivity might lead them to learn
higher-probability words more easily (Storkel, 2001). This explanation
is supported by computational simulations that show how learning general
phonotactics patterns create \enquote{well-worn paths} which allow the
models to represent several distinct but phonologically neighboring
words (Dell, Juliano, \& Govindjee, 1993; Siew, 2013; Takac, Knott, \&
Stokes, 2017). More generally, there is a growing interest in
investigating precisely how the local patterns acquired through
statistical learning may give rise to the global network orgnization
(For a review, see Karuza, Thompson-Schill, \& Bassett, 2016).

@@

This study investigated the class of nouns in isolation --- following
previous studies investigating the early semantic and phonological
network (Hills et al., 2009; Storkel, 2009). We could ask if studying
one class separtaly is a legitimate research strategy. In other words,
would word classes (such as nouns, verbs and function words) be acquired
relatively differently, or would they interact substantially to the
extent that it becomes unreasonable to study each class separately?

We know that different word classes follow different time trajectories.
For instance, in the early stages of development, nouns tend to be
acquired at a higher pace than predicates and function words (Bates et
al., 1994). Research has shown that this difference cannot be trivially
attributed to differences in the degree to which these classes are
present in the input; if anything, verbs and function words are often
more frequent in the input than nouns (e.g., Gentner, 1982). J. C.
Goodman et al. (2008) found an effect of frequency on the age of
acquisition within --- not across --- classes. Further, a recent work by
Braginsky et al. (2019) tested a large number of predictors, besides
frequency, and found that these predictors do not influence the
acquisition of word classes in the same way. For example, the
acquisition of nouns was found to be most influenced by frequency and
concreteness, whereas the acquisition of function words was most
influenced by word length.

These patterns support the hypothesis that different word classes have
different pathways of learning, thus making it worthwhile to study each
class separately. This hypothesis, however, does not preclude all sorts
of inter-class interaction. For example, Dautriche, Swingley, and
Christophe (2015) found that the acquisition of similar-sounding words
(\enquote{bih}-\enquote{dih}) is easier if these words belong to
different syntactic categories (e.g., a noun and a verb).

This work shares a number of limitations with previous studies using
similar research strategy and datasets. Chief among these limitations is
the fact that the age of word acquisition is computed using different
children at different ages (due to the fact that available CDI data is
mainly cross-sectional). Such a measure has been shown to be valid and
reliable (Fenson et al., 1994), and has allowed researchers to study
important aspects of word learning (Braginsky et al., 2019; J. C.
Goodman et al., 2008; Hills et al., 2009; Stella et al., 2017; Storkel,
2009). In our case, the use of cost-effective cross-sectional data has
allowed us to leverage large-scale studies across several languages.
That said, it is important to remember that this type of data can only
inform us about the learning trajectory of the \enquote{average} child.
Although our study endorses, overall, the externally-driven account of
network growth, this does not mean individual children never use some
variant of INT or some combination of both INT and EXT (Beckage \&
Colunga, under review). To illustrate, some children develop
\enquote{islands of expertise}, that is, well organized knowledge about
a certain topic (e.g., birds or dinosaurs). This prior knowledge enables
these children to learn new related words more easily (e.g., Chi \&
Koeske, 1983).

@@

@@

\clearpage

\section{Appendix A: Analyses using different phnonological
distances}\label{appendix-a-analyses-using-different-phnonological-distances}

In the methods section, we based the choice of setting the threshold of
edit distance at 2 on the fact that the early lexicon is very sparse in
terms of phonological neighborhood; the early proposal that set the
threshold at 1 (e.g., Vitevitch, 2008) was defined in the context of
rather mature, dense lexicon. Increasing the threshold from 1 to 2
allows for a more reasonable representation of the similarity space of
the early phonological network.

That said, it is useful to include the results obtained with both
thresholds. In addition, it could be useful to compare the results to
the case of weighted networks, i.e., with no thresholding. The main
analyses for these two cases are shown in what follows. In summary, both
methods of constructing the phonological networks had issues. While the
fact of using edit = 1 created sparsity, using weighted networks created
colinearity with length.

\subsection{Analyses using phonological networks constructed with an
edit distance of
1}\label{analyses-using-phonological-networks-constructed-with-an-edit-distance-of-1}

We show in Figure \ref{fig:corrPlot} the correlation between the
phonological connectivity and age of acquisition in both comprehension
and production. The sparsity issue, due the low phonological
neighborhood in the children's lexicon is apparent: most words had 0
degree and a few had non-zero but small degrees. The values of the
correlations are much lower than the ones obtained with the threshold of
2.

The next figures show how the phonology-based mechanism of growth
(phonoEXT) fares in comaprision to semEXT and other predictors of
learing in each language (Figure \ref{fig:staticPredEdit1} and across
all languages (Figure \ref{fig:staticAllEdit}). These figures show that
phonoEXT based on edit distance 1 had no noticeable effect on learning.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPlot-1} \caption{Age of acquistion in both comprehension and production as predicted by the degree (i.e., connectivity) in phonological network, using an edit distance of 1. Each point is a word, with lines indicating linear model fits, and numbers indicating the Pearson correlation coefficients.}\label{fig:corrPlot}
\end{figure}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllEdit-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined model. Here the phonologocal networks were based on an edit distance of 1. Results are shown for both production and comprehension data. Ranges indicate 95\% confidence intervals. Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.}\label{fig:staticAllEdit}
\end{figure}

\subsection{Analyses using wighted phonological networks with no
thresholding}\label{analyses-using-wighted-phonological-networks-with-no-thresholding}

We constructed weighted phonological networks where the edge between a
given pair of words \((w_1, w_2)\) was wieghted by
\(\frac{1}{edit(w_1,w_2)}\). The phonological connectivity of a given
word \(w\) was defined as the sum over all weighted edges with every
other word \(w_i\) in the network, i.e.,
\(\sum_{i} \frac{1}{edit(w,w_i)}\).

The results were as follows. On the one hand, the correlations were
generally high and in many cases (especially in the production data),
higher than the ones obtained with the thresholds 2 and 1 (Figure
\ref{fig:corrPlotnt}). On the other hand, phonoEXT resulted in very
noisy estimates when we controlled for frequency and length (Figures
\ref{fig:staticPrednt} and \ref{fig:staticAllnt}). The reason was that
the new phonological connectivity was very highly correlated with
length. The average correlation across languages was \(r =\) -0.95 for
production data (compared to -0.29 and -0.60 for the phonological
networks with edit = 1 and 2, respectvely). This fact lead to a
collinearity issue in the regression, making the effect hard to
estimate.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticAllnt-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined model. Here the phonologocal networks were based on weighted edges between words. Results are shown for both production and comprehension data. Ranges indicate 95\% confidence intervals. Dotted ranges indicate the estimates for the predictor in a separate model that includes only this predictor as a fixed effect.}\label{fig:staticAllnt}
\end{figure}

\clearpage

\section{Appendix B: Phonological connectivity across
languages}\label{appendix-b-phonological-connectivity-across-languages}

We were interested in investigating if, for a given meaning (e.g.,
\enquote{dog} in English and \enquote{chien} in French), phonological
connectivity varied across languages. For example, if \enquote{dog} is
highly connected in the English phonological network, will
\enquote{chien} also be highly connected in the French network, or will
these two forms be situated independently in their relative phonological
networks?

If the phonological networks are very similar across languages, then
network growth in the phonological domain may not be an independent
mechanism of acquisition, but rather an epiphenomenon of semantic-based
learning. If, instead, the phonological connectivity is different from
language to language, then this fact would lend support to phonological
growth being an independent driving mechanism of early word
learning.\footnote{Note that this question can also be answered through
  the models in Figures 5 and 6 where we test both semantic and
  phonological connectivities.}

To test this hypothesis, we compute the correlation of the unilemma's
phonological connectivity between every pair of languages. In Figure
\ref{fig:corrPair}, we plot the distribution of the pairwise pearson
correlation coefficent. Generally speaking, languages are not highly
correlated at the phonological level as the distributions peak at low
values of r, showing that phonological connectivily is not (at least not
fully) determined semantically.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/corrPair-1} \caption{The distribution of the Pearson correlation coefficents of the unilemma's phonological connectivity between every pair of languages.}\label{fig:corrPair}
\end{figure}

\newpage

@@

\hypertarget{ref-bates1994}{}
Bates, E., Marchman, V., Thal, D., Fenson, L., Dale, P., Reznick, J. S.,
\ldots{} Hartung, J. (1994). Developmental and stylistic variation in
the composition of early vocabulary. \emph{Journal of Child Language},
\emph{21}(1).

@@

\hypertarget{ref-braginsky2019}{}
Braginsky, M., Yurovsky, D., Marchman, V. A., \& Frank, M. C. (2019).
Consistency and variability in children?s word learning across
languages. \emph{Open Mind}, \emph{3}.

@@

\hypertarget{ref-dautriche2015}{}
Dautriche, I., Swingley, D., \& Christophe, A. (2015). Learning novel
phonological neighbors: Syntactic category matters. \emph{Cognition},
\emph{143}.

@@

\hypertarget{ref-gentner1982}{}
Gentner, D. (1982). Why nouns are learned before verbs: Linguistic
relativity versus natural partitioning. \emph{Center for the Study of
Reading Technical Report}.

@@

\hypertarget{ref-karuza2016}{}
Karuza, E. A., Thompson-Schill, S. L., \& Bassett, D. S. (2016). Local
patterns to global architectures: Influences of network topology on
human learning. \emph{Trends in Cognitive Sciences}, \emph{20}(8).

@@

\hypertarget{ref-siew2013}{}
Siew, C. S. (2013). Community structure in the phonological network.
\emph{Frontiers in Psychology}, \emph{4}.

### 2019-09-20 main_analyses.Rmd
revisions

@@

@@

  phono_pairs<- make_IPA_pairs(def_list = def_list, lang = lang) %>%
    mutate(language = lang) %>%
    left_join(item_unilemma) %>%
    rename(item0 = item,
           item = pair,
           item.uni_lemma = uni_lemma) %>%
    left_join(item_unilemma) %>%
    rename(pair.uni_lemma = uni_lemma,
           pair = item,
           item = item0)

@@

feather::write_feather(phono_pairs_all, "saved_data/phono_pairs_all.feather")

@@

#Pairwise comparision: each time, take the overlap and do the test

data_prod <- data_aoa %>%
  filter(measure =='produces')

data_by_lang <- split(phono_pairs_dist$language)

@@

  lang1_unilemmas <- unique(lang1$uni_lemma)
  lang2_unilemmas <- unique(lang2$uni_lemma)
  uni_intersect <-  intersect(lang1_unilemmas, lang2_unilemmas)

  data_lang1 <- lang1 %>%
    filter(!is.na(uni_lemma),
           uni_lemma %in% uni_intersect) %>%
    select(uni_lemma, aoa) %>%
    group_by(uni_lemma) %>%
    summarise(aoa1=mean(aoa))

@@

}
  map(data_by_lang, pair_cor_data) %>%
    bind_rows()

>>>>

phono_red <- feather::read_feather("saved_data/phono_red_nt.feather")

data_by_lang <- phono_red %>%
  filter(measure =="produces") %>%
  split(.$language)

  lang1_unilemmas <- unique(lang1$uni_lemma)
  lang2_unilemmas <- unique(lang2$uni_lemma)

  uni_intersect <-  intersect(lang1_unilemmas, lang2_unilemmas)

  data_lang1 <- lang1 %>%
    filter(!is.na(uni_lemma), 
           !is.na(PAC_phono),
           PAC_phono != "Inf",
           uni_lemma %in% uni_intersect) %>%
    select(uni_lemma, PAC_phono) %>%
    group_by(uni_lemma) %>%
    summarise(deg_lang1 = mean(PAC_phono))

  data_lang2 <- lang2 %>%
    filter(!is.na(uni_lemma), 
           !is.na(PAC_phono),
           PAC_phono != "Inf",
           uni_lemma %in% uni_intersect) %>%
    select(uni_lemma, PAC_phono) %>%
    group_by(uni_lemma) %>%
    summarise(deg_lang2 = mean(PAC_phono_t2))

  mycorr <- cor.test(both$deg_lang1, both$deg_lang2)

  val=mycorr$estimate
  p=mycorr$p.value

  language1 = unique(lang1$language) 
  language2 = unique(lang2$language)

  }
  map(data_by_lang, pair_cor_data) %>%
    bind_rows()
}

cor_data <- map(data_by_lang, pair_data) %>%
  bind_rows() %>%
  filter(language1!=language2) %>%
  mutate(data="languages")

#feather::write_feather(cor_data, "saved_data/cor_data.feather")
cor_data <- feather::read_feather("saved_data/cor_data.feather")

plots
```{r}

ggplot(cor_data, 
      aes(x = tau)) +
  geom_histogram(aes(y = (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
                 alpha=0.5,
                 binwidth=0.1)+
  #scale_x_log10() +
  theme_few() + 
  theme(aspect.ratio = 0.7, legend.title = element_text(size=8)) +  #facet_grid(Segmentation ~ language)+
  scale_y_continuous(labels = scales::percent)+
  xlab("pairwise correlation") +ylab("Count")

@@

  lang <- unique(growth_meas_lang$language)
  meas <- unique(growth_meas_lang$measure)

@@

  phono_pairs<- make_IPA_pairs(def_list = def_list, lang = lang) %>%
    mutate(language = lang, 
           measure = meas) %>%
    left_join(item_unilemma) %>%
    rename(item0 = item,
           item = pair,
           item.uni_lemma = uni_lemma) %>%
    left_join(item_unilemma) %>%
    rename(pair.uni_lemma = uni_lemma,
           pair = item,
           item = item0)

@@

@@

#phono_pairs_wide <- phono_pairs_dist %>%
 # spread(language, dist)
#Pairwise comparision: each time, take the overlap and do the test

phono_pairs_produce <- phono_pairs_dist %>%
  filter(measure == "produces")

data_by_lang <- phono_pairs_produce %>% 
  split(.$language)

@@

  lang1_unilemmas <- unique(lang1$item.uni_lemma)
  lang2_unilemmas <- unique(lang2$item.uni_lemma)

  uni_intersect <-  intersect(lang1_unilemmas, lang2_unilemmas)

  data_lang1 <- lang1 %>%
    filter(item.uni_lemma %in% uni_intersect,
           pair.uni_lemma %in% uni_intersect) %>%
    select(item.uni_lemma, pair.uni_lemma, link2) %>%
    rename(link2_lang1 = link2)

  data_lang2 <- lang2 %>%
    filter(item.uni_lemma %in% uni_intersect,
           pair.uni_lemma %in% uni_intersect) %>%
    select(item.uni_lemma, pair.uni_lemma, link2) %>%
    rename(link2_lang2 = link2)

  data_both <- data_lang1 %>%
    left_join(data_lang2)

  #data_mat <- acast(data_both, item.uni_lemma~pair.uni_lemma, value.var="link2_lang1")

  #This too costly computationnally speaking, will try the one-dimentional analysis instead, it should be enough

@@

}
  map(data_by_lang, pair_cor_data) %>%
    bind_rows()
}

cor_data <- map(growth_by_meas_lang, pair_data) %>%
  bind_rows() %>%
  filter(language1!=language2) %>%
  mutate(data="languages")

Here I will do the analysis for the power law (less computation-costly and more relant to the rest of the analyses)
